\documentclass[11pt]{tingpset}

\Name                   {Michaels Tingley and Traver}
\Email                  {\{michaeltingley, mtraver\}@college.harvard.edu}
\Organization           {Harvard University}
\Class                  {Computer Science 175}
\ClassShort             {CS175}
\ProblemSetNumber       {9}
\DueDate                {25 November 2013, 11:59pm}
\CollaborationStatement {Michaels Tingley and Traver completed this problem set in tandem.}

\begin{document}
  \makeheader

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \problem
    Image B is the only viable image. Here's why.

    First, let's consider what it means to change the field of view. As read in section 10.3, a change in the field of view of $\theta$ degrees is the same as applying a scale of $-n = \frac{1}{\tan \frac{\theta}{2}}$. Thus, any transformation of the view of the cube must be consistent with a scale. Thus, it is clear that \textbf{B} is consistent with this --- as the front face of the cube grows in size, the rear face grows slower. However, the growth speed of both is proportional. That is, if the front face grows by 20\%, the back also appears to grow by 20\%. This is consistent with a change of scale.

    Meanwhile, this proportional growth rate is not maintained by answers \textbf{A} and \textbf{C}. In answer \textbf{A}, the rear face does not grow at all. In addition to this not being consistent, it begs the following question: \emph{what is happening on behind the rear face?} That is, if we had a third face that was behind the rear cube face, it's unclear what it would do... answer \textbf{A} may even imply that it would \emph{shrink}, which is clearly wrong. Answer \textbf{C} also doesn't make sense, because the back face grows faster than the front face. This doesn't make any sense; in addition to this not being consistent with proportionate growth, it begs the following question: \emph{what happens if we decreased the field of view even more?} If it were to continue with this trend, the rear face would grow larger the the front face... which doesn't make geometric sense at all.

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \problem

  \todo

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \problem

  \todo

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% 4 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \problem

  \todo

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% 5 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \problem

  \todo

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% 6 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \problem

  \todo

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% 7 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \problem

  \todo

\end{document}
